### 2013-07-06 cws/emnlp_cws/discussion.tex
minor fixes
everything but stats-sig test results

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.
On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
In 77.4\% of the cases, DD converged in the first iteration. For the remaining cases, the number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{histogram.png}
\caption{No. of iterations till DD convergence histogram.}
\label{fig:histo}
\end{center}
\end{figure}

@@

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or polling-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
\begin{small}
\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{small}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.
%
%gold: 在 李鄭屋邨 附近
%CRF: 在 李鄭屋邨 附近
%PCT: 在 李鄭屋 邨 附近   <-- DD
%
%gold: 麥 父 笑說
%CRF:  麥 父 笑說
%PCT: 麥父 笑說    <-- DD
%
%gold: 天氣 熱 時 冷氣 大 開     
%CRF: 天氣 熱 時 冷氣 大 開     
%PCT: 天氣 熱時 冷氣 大 開     <-- DD

>>>>

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.

@@

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
\begin{small}
\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{small}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{histogram.png}
\caption{No. of iterations till DD convergence.}
\label{fig:histo}
\end{center}
\end{figure}

%
%gold: 在 李鄭屋邨 附近
%CRF: 在 李鄭屋邨 附近
%PCT: 在 李鄭屋 邨 附近   <-- DD
%
%gold: 麥 父 笑說
%CRF:  麥 父 笑說
%PCT: 麥父 笑說    <-- DD
%
%gold: 天氣 熱 時 冷氣 大 開     
%CRF: 天氣 熱 時 冷氣 大 開     
%PCT: 天氣 熱時 冷氣 大 開     <-- DD

### 2013-07-06 cws/emnlp_cws/experiment.tex
everything but stats-sig test results

In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.

For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
and sigma set to 3.

For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.

For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.

% question: what is the relationship between this dev data and that used in sighan2003/2005?
We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.

\subsection{Datasets}
We run our experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. Specifically, we use the standard training and test splits for the 2003 Academia Sinica (AS), Peking University (PU), and City University of Hong Kong (CU) datasets as well as the 2005 AS, PU, CU, and Microsoft Research (MSR) datasets. We do not use the 2003 Chinese Treebank dataset because... [why exactly?]

%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

%
%\begin{table}
%\centering
%\begin{small}
%\begin{tabular}{ l | l | c | c | c | c | c   }
%%\cline{2-10}
%%\hline
%% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No. of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
%\hline
%    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
%\hline
%\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
%& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
%& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
%& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
%\hline
%\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
%& PU  &  - & - & - & - & 6.9 \\
%& CU  & - & - & - & - & 7.1  \\
%%\hline
%%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
%%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
%%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
%%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\
%
%\end{tabular} 
%\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
%\end{small}
%\end{table}

>>>>

We conduct experiments  on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1. Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}. They have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
everything but stats-sig test results

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. \newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans. Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

>>>>

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. \newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans. Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

### 2013-07-06 cws/emnlp_cws/models.tex
minor fixes
everything but stats-sig test results

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp^{ \vec\theta \vec{f}(x, y_{t}, y_{t+1}) } }}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
But the Markov assumption in CRF limits the context of such features, it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

\subsection{Word-based Models}
Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. More recent success was reported by  \newcite{Zhang:2007:ACL}, who used a linear discriminative model to score candidate word lists. 
More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
\begin{align*}
F(\mathbf{y}|\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{\mathbf{y}}) }
\end{align*}
\noindent Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}. Searching through the entire  search space $\mathrm{GEN}(\mathbf{x})$ is intractable even with a local model. A beam-search algorithm is therefore employed. The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypothesis by either appending the new character to the last word in the beam, or start a new word at current position.

\begin{algorithm}[!ht]
\begin{footnotesize}
\caption{DD inference algorithm, modified Viterbi and BeamSearch.}
\begin{algorithmic}
\STATE $\forall i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} \colon \; \forall k \in \{0,1\} \colon u_{i}(k) = 0$
\FOR{$t \leftarrow 1$  \textbf{to} $T$}
\STATE   $\mathbf{y^{c*}} = \argmaxb \; P(\mathbf{y^\textit{c}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c})}$ 
\STATE   $\mathbf{y^{w*}} = \argmax \; F(\mathbf{y^\textit{w}} | \mathbf{x}) -  \sum\limits_{i\in |\mathbf{x}|}{ u_{i}(y_j^\textit{w})}$
\IF{ $\mathbf{y^{c*}} =  \mathbf{y^{w*}}$ }
\RETURN $\left(\mathbf{y^{\textit{c}*}},\mathbf{y^{\textit{w}*}}\right)$
\ENDIF
\FORALL{$i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} $}
\STATE  $\forall k \in \{0,1\}: u_i(k)=u_i(k) + \alpha_t (2k-1)(y_i^{w*}-y_i^{c*})$ 
\ENDFOR
\ENDFOR
\RETURN $\left(\mathbf{y^{c*}},\mathbf{y^{w*}}\right)$
 \\\hrulefill
\STATE Viterbi: 
\STATE $V_1(1) = 1, V_1(0) = 0$
\FOR{$i = 2 \; \mathrm{to} \; |\mathbf{x}|$}
\STATE $\forall k \in \{0,1\}: V_i(k) = \argmaxk P_i(k | k') V_{i-1}{k'} + u_{i}(k)$ 
\ENDFOR
 \\\hrulefill
\STATE BeamSearch:
\FOR{$i = 1 \; \mathrm{to} \; |\mathbf{x}|$}
\FOR{ item $v = \{w_0,\cdots,w_j\}$ in $\mathrm{beam}(i)$}
\STATE append $x_i$ to $w_j$, $\mathrm{score}(v) \stackrel{+}{=}   u_{i}(0)$
\STATE $v = \{w_0,\cdots,w_j, x_i\}$, $\mathrm{score}(v) \stackrel{+}{=} u_{i}(1)$
\ENDFOR
\ENDFOR
\end{algorithmic}
\label{algo:DD}
\end{footnotesize}
\end{algorithm}

\subsection{Combine Models with Dual-decomposition} 
Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

@@

The high-level idea is that jointly model both character-sequence and word information can be difficult, so instead we explore the joint search space at inference time to find an output that the two models are most likely to agree.
Formally, the objective that DD optimizes is:
\begin{align*}
   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
\end{align*}
\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algorithm~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

>>>>

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}\vspace{-10em}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
\vspace{-10em}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
But the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

\subsection{Word-based Models}
Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. 
 \newcite{Zhang:2007:ACL} reported more recent success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
 Formally, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
\begin{align*}
F(\mathbf{y}|\mathbf{x}) =  \argmax{ \left( \alpha \cdot \phi(\mathbf{\mathbf{y}}) \right) }
\end{align*}
\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model. A beam-search algorithm is therefore employed. The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or start a new word at current position.

\begin{algorithm}[!ht]
\begin{footnotesize}
\caption{DD inference algorithm, modified Viterbi and beam-search.}
\begin{algorithmic}
\STATE $\forall i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} \colon \; \forall k \in \{0,1\} \colon u_{i}(k) = 0$
\FOR{$t \leftarrow 1$  \textbf{to} $T$}
\STATE   $\mathbf{y^{c*}} = \argmaxb \; P(\mathbf{y^\textit{c}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c})}$ 
\STATE   $\mathbf{y^{w*}} = \argmax \; F(\mathbf{y^\textit{w}} | \mathbf{x}) -  \sum\limits_{i\in |\mathbf{x}|}{ u_{i}(y_j^\textit{w})}$
\IF{ $\mathbf{y^{c*}} =  \mathbf{y^{w*}}$ }
\RETURN $\left(\mathbf{y^{\textit{c}*}},\mathbf{y^{\textit{w}*}}\right)$
\ENDIF
\FORALL{$i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} $}
\STATE  $\forall k \in \{0,1\}: u_i(k)=u_i(k) + \alpha_t (2k-1)(y_i^{w*}-y_i^{c*})$ 
\ENDFOR
\ENDFOR
\RETURN $\left(\mathbf{y^{c*}},\mathbf{y^{w*}}\right)$
 \\\hrulefill
\STATE Viterbi: 
\STATE $V_1(1) = 1, V_1(0) = 0$
\FOR{$i = 2 \; \mathrm{to} \; |\mathbf{x}|$}
\STATE $\forall k \in \{0,1\}: V_i(k) = \argmaxk P_i(k | k') V_{i-1}{k'} + u_{i}(k)$ 
\ENDFOR
 \\\hrulefill
\STATE Beam-Search:
\FOR{$i = 1 \; \mathrm{to} \; |\mathbf{x}|$}
\FOR{ item $v = \{w_0,\cdots,w_j\}$ in $\mathrm{beam}(i)$}
\STATE append $x_i$ to $w_j$, $\mathrm{score}(v) \stackrel{+}{=}   u_{i}(0)$
\STATE $v = \{w_0,\cdots,w_j, x_i\}$, $\mathrm{score}(v) \stackrel{+}{=} u_{i}(1)$
\ENDFOR
\ENDFOR
\end{algorithmic}
\label{algo:DD}
\end{footnotesize}
\end{algorithm}

\begin{table*}
\centering
\begin{small}
\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{AS} &  \multicolumn{5}{c}{PU} \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\ 
Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064  &  94.6 &	95.3 & 94.9  &   77.8   & 0.089    \\
Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
%\cline{2-9}
\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{CU} &  \multicolumn{5}{c}{MSR}  \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\ 
Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7  & 0.073 &  97.0 &  97.2 & 97.1  & 74.6 & 0.063  \\
Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
\end{tabular} 
\caption{Results on SIGHAN 2005 datasets. {R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency. $\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. }\label{tbl:results}
\end{small}
\end{table*}

\subsection{Combine Models with Dual Decomposition} 
Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

@@

The idea is that jointly model both character-sequence and word information can be computationally challenging,  instead we could try to find outputs that the two models are most likely to agree on.
Formally, the objective of DD is:
\begin{align*}
   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
\end{align*}
\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.
